---
output: github_document
---


```{r, include = FALSE}
options(repos = c(CRAN = "https://cloud.r-project.org/"))  # Set CRAN mirror
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# STAT 545 Assignment B-2: 
## Package: ANOVA.TukeyHSD
#### Student: Martin Moran (48449193)
#### Deadline: November 8 @5:00pm PDT

<!-- badges: start -->
![MIT License](https://img.shields.io/badge/license-MIT-brightgreen.svg)
<!-- badges: end -->


## Assignment B-2
Assignment B-2 is an individual project as part of the STAT 545B coursework. Through this project, I will package my function that I made during Assignment B-1.

##### The Files in this Repository Include: README.md/.Rmd, NAMESPACE, DESCRIPTION, R/ANOVA.TukeyHSD.R, man/ANOVA.TukeyHSD.Rd, tests/testthat/testthat-ANOVA.TukeyHSD.R, and inst/extdata.xlsx. 
* The **README** files contain background information on the project and the components included in this repository.
* The **NAMESPACE** file defines which functions are accessible to users and specifies package dependencies, controlling the import and export of functions.
* The **DESCRIPTION** file contains metadata about the package, including its name, version, author, dependencies, and a brief description of its purpose.
* The **R/ANOVA.TukeyHSD.R** file contains the core function code for the the ANOVA.TukeyHSD package.
* The **man/ANOVA.TukeyHSD.Rd** file provides a detailed explanation of the function’s purpose, parameters, usage, and example code.
* The **tests/testthat/testthat-ANOVA.TukeyHSD.R** file contains unit tests for the ANOVA.TukeyHSD function, verifying that the function behaves as expected with various inputs.
* The **inst/extdata.xlsx** file is the data set that I have been using since the mini-data analysis in section A. It is included in this repository because it is used in the testthat-ANOVA.TukeyHSD.R file.

## Package Description
The packaged function performs an ANOVA statistical analysis and Tukey's Honestly Significant Difference (HSD) Post Hoc Test. This function streamlines the analysis workflow by combining two commonly used statistical tests into one simple command.

## Install Instructions
To use the ANOVA.TukeyHSD() function, install the package using github_install() from devtools as shown below:

1. Install devtools (if not already installed):
```{r, eval = FALSE}
install.packages("devtools")
```

2. Load devtools:
```{r, include = TRUE, message = FALSE, warning = FALSE}
library(devtools)
```
3. Install this package from github:
```{r, include = TRUE, message = FALSE, warning = FALSE}
install_github("stat545ubc-2024/assignment-b2-mpmoran1234")
```

## Demonstrated Usage / Example
Here’s an example of how to use the ANOVA.TukeyHSD function with sample data:
```{r}
# Load the package
library(ANOVA.TukeyHSD)
  
# Sample data frame
data <- data.frame(
group = rep(letters[1:3], each = 10),
value = c(rnorm(10, mean = 5), rnorm(10, mean = 7), rnorm(10, mean = 6))
)
  
# Run the ANOVA and Tukey HSD tests
result <- ANOVA.TukeyHSD(data, value ~ group)
  
# View the results
print(result)
```

